Kindly Bent to Free Us

### 2020-02-28 kindly/main.tex
Use the ICFP format.
Adapt the figures to fit better.
Move back the sudoku example.
abstract

\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[sigplan,10pt,review,anonymous]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

\mprset{sep=1.2em}

@@

  While statically typed programming languages guarantee type soundness and memory
  safety by design, most of them do not address issues arising
  from improper resource handling.
  Linear and affine types guarantee single-threaded resource usage,
  but they are rarely deployed as they are too restrictive for real-world applications.

  We present \lang, an extension of ML with constrained types that
  manages linearity and affinity properties through kinds. In addition
  \lang{} supports the exclusive and shared borrowing of affine
  resources, inspired by features of Rust.
  Moreover, \lang{} retains the defining features of the ML family:
  an impure, strict, functional expression language with complete principal type
  inference and type abstraction.
  \lang does not require any linearity annotations in
  expressions and supports common functional programming idioms.
\end{abstract}

@@

\section{Further Examples}
\label{sec:extra-example}
\lstMakeShortInline[keepspaces,basicstyle=\small\ttfamily]@
\input{motivation-linearity}
\input{motivation-persistent}
\input{motivation-pool}
\lstDeleteShortInline@

>>>>

\PassOptionsToPackage{svgnames}{xcolor}
\documentclass[acmsmall,review,anonymous]{acmart}
\settopmatter{printfolios=true,printccs=false,printacmref=false}

@@

\mprset{sep=1.5em}

@@

  While statically typed programming languages guarantee type soundness and memory
  safety by design, most of them do not address issues arising
  from improper handling of resources.
  An important step towards handling resources is the adoption of 
  linear and affine types that enforce single-threaded resource usage.
  However, the few languages supporting such types require heavy type
  annotations.

  We present \lang, an extension of ML that
  manages linearity and affinity properties using kinds and
  constrained types. In addition
  \lang{} supports the exclusive and shared borrowing of affine
  resources, inspired by features of Rust.
  Moreover, \lang{} retains the defining features of the ML family:
  it is an impure, strict, functional expression language with complete principal type
  inference and type abstraction.
  \lang{} does not require any linearity annotations in
  expressions and supports common functional programming idioms.
\end{abstract}

@@

\section{Further Examples}
\label{sec:extra-example}
\lstMakeShortInline[keepspaces,basicstyle=\small\ttfamily]@
\input{motivation-linearity}
\input{motivation-pool}
\lstDeleteShortInline@
